\documentclass{beamer}
\hypersetup{pdfpagemode=FullScreen}
\usepackage[utf8x]{inputenc}
\usepackage[czech]{babel}
\usetheme[pageofpages=of,% String used between the current page and the
                         % total page count.
          bullet=circle,% Use circles instead of squares for bullets.
          titleline=true,% Show a line below the frame title.
	  titlepagelogo=opensuse,
          alternativetitlepage=true,% Use the fancy title page.
          ]{Torino}
\usepackage{fontspec}
\setmainfont{Liberation Sans}
\author{Tom\'{a}\v{s} Chv\'{a}tal et al.\newline {\small tchvatal@suse.com}\newline {\small SUSE/L3 - Packaging}}
\title{Future of the software packaging}
\date{2018/10/06}

\AtBeginSection[]
{
	\setbeamercolor{background canvas}{bg=chameleongreen0}
	\begin{frame}[plain]
		\begin{center}\begin{huge}\textcolor{white}{\secname}\end{huge}\end{center}
	\end{frame}
	\setbeamercolor{background canvas}{bg=}
}

\AtBeginSubsection[]
{
	\setbeamercolor{background canvas}{bg=chameleongreen0}
	\begin{frame}[plain]
		\begin{center}\begin{huge}\textcolor{white}{\subsecname}\end{huge}\end{center}
	\end{frame}
	\setbeamercolor{background canvas}{bg=}
}

\begin{document}

\begin{frame}[t,plain]
\titlepage
\end{frame}

\section{Introduction}

\begin{frame}[t]{Who}
    \begin{center}Who the hell is this sod presenting here?\end{center}
	\begin{itemize}
	\item SUSE employee working as torturer^Wteamlead of Packaging team
    \item One of the people that created Tumbleweed rolling release distro
    \item Formely Gentoo developer and Council member
	\end{itemize}
\end{frame}

\begin{frame}[t]{What}
	\begin{itemize}
	\item First we will dig up some brief history of the packaging
    \item Then we will check up on why do we even bother with the work
    \item And at the end we will make fun of everyone else, or should we?
	\end{itemize}
\end{frame}

\section{Why bother}

\begin{frame}[t]{What actually is packaging}
	\begin{itemize}
	\item Postal services, software? It does not matter.
	\item The core goal is to get something that can be trusted from point A to B
	\end{itemize}
\end{frame}

\begin{frame}[t]{Packages}
	\begin{center}Most operating systems have some type of packaging\end{center}
    \begin{itemize}
      \item Unix/Linux - yours truly RPM/ebuild/packman/\ldots
      \item Windows - nsis wizzards/MSI archives/\ldots
      \item Mac - the app bundles
    \end{itemize}
\end{frame}

\begin{frame}[t]{Languages}
  \begin{itemize}Many popular languages have their own package system/registry\end{center}
    \begin{itemize}
      \item CPAN (perl)
      \item pypi (python)
      \item cabal (haskell)
      \item npm (JS)
    \end{itemize}
\end{frame}

\begin{frame}[t]{Why do we need packages at all?}
	\begin{itemize}
	\item We need to be able to deliver software to users
    \item We need to isolate required components
	\item We need to ensure proper testing of the components
	\item We need to compile all various software stacks together
	\item We need to provide comprehensive solutions for some tasks
    \begin{itemize}
      \item Dependencies
      \item Updating and migration
      \item User management
      \item Post-installation configuration (first config, no wizzards)
    \end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}[t]{Packages on Linux}
	\begin{itemize}
	\item Most distributions are leveraging some package/software management
    \begin{itemize}
      \item Debian/Ubuntu (apt + dpkg)
      \item Arch linux (pacman)
      \item Gentoo linux (portage)
      \item rpm based distributions (rpm + zypper/yum/dnf)
    \end{itemize}
  \end{itemize}
\end{frame}


\begin{frame}[t]{What are packages for the user?}
	\begin{itemize}
	\item Collection of files and their respective permissions
	\item Metadata containing information about the software runtime dependencies
	\item Initial configuration provider
	\end{itemize}
\end{frame}

\section{Bit of history}

# 1995
# 2000
# 2010
# NOW

\section{Future?}
# FLATPACK/Appimage
# containers and their updates


\section{Endnote}
# recap of why packaging is important
# invitation to contribute

\begin{frame}{Thanks/Questions}
	\begin{center}
	Thank you for your attention.\\
	Are there any questions?
	\end{center}
\end{frame}

\end{document}

